Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
replaced "e.g." by "e.g.,"

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis 
  from a transfer function representation into a state space representation. 
  Such representation allows to study the  input-to-state dynamics, while 
  transfer functions represents only input-output relations and cannot be 
  enough to ensure deeper properties, e.g. the safety property.
%
\item We proposes a synthesis of state feedback controllers that ensures 
  safety properties, that is only  possible in state-space representation. 
  In addition to the already existing stability conditions which is a much 
  harder problem.
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase 
  speed whilst retaining soundness. Both approaches provide sound
  synthesis of state feedback systems considering the various
  error sources in the implementation of the control algorithm and in the
  computational modelling of plant dynamics.
%
\item We develop a model for different sources quantization and their
  effect on the state space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}

@@

In particular, Jury stability test is already explained in the control system 
literature ({\it e.g.}~\cite{fadali}). This study, however, limits itself to 
explain the encoding of Jury's criterion for the formal synthesis purpose. 
For the stability  test procedure, the following Jury matrix 
$M=[m_{ij}]_{(2N-2)\times N}$ is built  from $P(z)$ coefficients:
$$
M=\left[
\begin{matrix}
  V^{(0)} \\
  V^{(1)} \\
  \vdots \\
  V^{(N-2)}
 \end{matrix}
\right]\mbox{,}
$$
\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ such that
$$
v^{(0)}_{ij}=\begin{cases} 
a_{j-1}, & \mbox{if } i=1 \\   v^{(0)}_{(1)(N-j+1)}, & \mbox{if } i=2 
\end{cases}\mbox{, and} 
$$
$$
v^{(k)}_{ij}=\begin{cases} 
0, & \mbox{if } j>n-k\\
v^{(k-1)}_{1j}-v^{(k-1)}_{2j}\cdot\frac{v^{(k-1)}_{11}}{v^{(k-1)}_{21}}, & \mbox{if } j\leq n-k  \mbox{ and } i=1 \\
v^{(k)}_{(1)(N-j+1)}, & \mbox{if } j\leq n-k \mbox{ and } i=2 \\
\end{cases} \mbox{,}
$$
\noindent where $k\in\mathbb{Z}$, such that $0<k<N-2$. $P(z)$ is the 
characteristic polynomial of a stable system if and only if the following 
four propositions hold:
\begin{itemize}
\item $R_{1}$: $P(1)>0$;
\item $R_{2}$: $(-1)^{N}P(-1)>0$;
\item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
\item $R_{4}$: $m_{11}>0\iff (m_{31}>0)\wedge (m_{51}>0)\wedge \dots \wedge (m_{(2N-3)(1)>0)}$.
\end{itemize}

>>>>

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis 
  from a transfer function representation into a state space representation. 
  Such representation allows to study the  input-to-state dynamics, while 
  transfer functions represents only input-output relations and cannot be 
  enough to ensure deeper properties, e.g., the safety property.
%
\item We proposes a synthesis of state feedback controllers that ensures 
  safety properties, that is only  possible in state-space representation. 
  In addition to the already existing stability conditions which is a much 
  harder problem.
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase 
  speed whilst retaining soundness. Both approaches provide sound
  synthesis of state feedback systems considering the various
  error sources in the implementation of the control algorithm and in the
  computational modelling of plant dynamics.
%
\item We develop a model for different sources quantization and their
  effect on the state space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}

@@

In particular, Jury stability test is already explained in the control system 
literature ({\it e.g.},~\cite{fadali}). This study, however, limits itself to 
explain the encoding of Jury's criterion for the formal synthesis purpose. 
For the stability  test procedure, the following Jury matrix 
$M=[m_{ij}]_{(2N-2)\times N}$ is built  from $P(z)$ coefficients:
$$
M=\left[
\begin{matrix}
  V^{(0)} \\
  V^{(1)} \\
  \vdots \\
  V^{(N-2)}
 \end{matrix}
\right]\mbox{,}
$$
\noindent where $V^{(k)}=[v^{(k)}_{ij}]_{2\times N}$ such that
$$
v^{(0)}_{ij}=\begin{cases} 
a_{j-1}, & \mbox{if } i=1 \\   v^{(0)}_{(1)(N-j+1)}, & \mbox{if } i=2 
\end{cases}\mbox{, and} 
$$
$$
v^{(k)}_{ij}=\begin{cases} 
0, & \mbox{if } j>n-k\\
v^{(k-1)}_{1j}-v^{(k-1)}_{2j}\cdot\frac{v^{(k-1)}_{11}}{v^{(k-1)}_{21}}, & \mbox{if } j\leq n-k  \mbox{ and } i=1 \\
v^{(k)}_{(1)(N-j+1)}, & \mbox{if } j\leq n-k \mbox{ and } i=2 \\
\end{cases} \mbox{,}
$$
\noindent where $k\in\mathbb{Z}$, such that $0<k<N-2$. $P(z)$ is the 
characteristic polynomial of a stable system if and only if the following 
four propositions hold:
\begin{itemize}
\item $R_{1}$: $P(1)>0$;
\item $R_{2}$: $(-1)^{N}P(-1)>0$;
\item $R_{3}$: $\vert{a_{0}}\vert <a_{N}$;
\item $R_{4}$: $m_{11}>0\iff (m_{31}>0)\wedge (m_{51}>0)\wedge \dots \wedge (m_{(2N-3)(1)>0)}$.
\end{itemize}
